---
title: "FastQC"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
####Running FASTQC
This was run on the mac computer upstairs. The output files from running FastQC were 3 matrices each with different types of statistics. The output is saved in my FASTQC folder on the M Drive.

####Install fastqcr and tibble packages
```{r eval=FALSE, include=FALSE}
#install.packages("fastqcr")
library("fastqcr")
#install.packages("tibble")
library("tibble")
```

####Run fastqc through R
qc_aggreate combines information from zip files into 1 matrix,
summary generates a table of pass/fail/warn for different QC categories, qc_stats generates a date frame with general statistics of fastqc reports
```{r eval=FALSE, include=FALSE}
##This ran about 30 mins for 66 samples
# This portion of the script was written for the MAC comp upstairs.
qc.dir = "/Volumes/Data_02/AshleyGallagher/FASTQC"
fastqc(fq.dir=get(wd),qc.dir,threads=4)
QCtable<-qc_aggregate(qc.dir, progressbar=TRUE)
Pass_fail<-summary(QCtable)
qc_stats_table<-qc_stats(QCtable)

```

```{r}

```

#### Analyzing fastqc data
Figure 1: Number of sequences with pass/fail/warning status
```{r pressure, echo=FALSE, fig.cap="Graph showing the number of samples that passed, failed or should be considered with caution on a number of different QC criteria. "}

d<-t(Pass_fail[,c(4,5,3)])
op <- par(mar=c(11,4,4,2))
barplot(as.matrix(d), names.arg = Pass_fail$module, las=2, ylab="Number of samples", main = "Quality control using FastQC",col=c("green","yellow","red"),legend=c("Pass","Warn","Fail"),cex.names=0.8)

###for an unstacked bar plot
barplot(as.matrix(d), names.arg = Pass_fail$module, las=2, ylab="Number of samples", main = "Quality control using FastQC",col=c("green","yellow","red"),cex.names=0.8,beside=TRUE)
legend(35, 65, c("Pass","Warn","Fail" ), fill=c("green","yellow","red" ))

```


Graphing the reads per sample
```{r}
a<-qc_stats_table
a$sample<-gsub("\\-.*","",a$sample)
plot(a$tot.seq~a$sample, type="h", col="blue", xlab="sample number", ylab="number of sequenced reads", main="Sequenced reads per sample", lwd=3, lty=1)
abline(h=mean(as.numeric(a$tot.seq)))
abline(h=mean(as.numeric(a$tot.seq))-sd(as.numeric(a$tot.seq)), col="red", lty=2)
abline(h=mean(as.numeric(a$tot.seq))+sd(as.numeric(a$tot.seq)), col="red", lty=2)
legend(46,34500000, c("Mean","Standard deviation"), lty=c(1,3),col=c("black","red"))

mean(as.numeric(a$tot.seq))
# 11119433
sd(as.numeric(a$tot.seq))
# 6204685

```

Sorts by tot.seq
```{r}
indices<-sort(a$tot.seq, index=TRUE)
a[indices$ix,]

```






